A new metric for automatic data visualization for distributional difference in time series

### 2021-05-11 paper/main.Rmd
separating codes from text

---
title: A new metric for automatic discovery of periodic patterns in time series

@@

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE,
        tinytex.verbose = FALSE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
#library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)
library(kableExtra)
library(distributional)
library(ggplot2)
library(sugrrants)
library(here)
library(ggplot2)
library(patchwork)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
#                                                                read_chunk('main.R')
here::here()
#knitr::read_chunk(here::here("paper/R/", "null_distribution.R"))
#knitr::read_chunk(here::here("paper/R/", "mean_null.R"))
#source(here::here("paper/R/sim_panel.R"))
# Set up plan
#source("_drake.R")
# Run all code required
#drake::r_make()
# load each object as required
# loadd()
```

@@

```{r calendar-elec, fig.height = 8, fig.cap = "Calendar displays faceted by two households are shown. The calendar displays are rich in information and has several components. For example, it can be observed easily that the level of energy consumption by household 2 is higher than household 4. Also, it gives an overview on when these households are away for holidays and which months consumptions are highest (Jan, Feb). However, when it comes to discerning periodic patterns, analyzing all possible periodic patterns through this display is overwhelming due to combination of linear and cyclic representation of time. For example, there is more going on in terms of peaks and troughs in id 2 compared to id 4, but it is not clear which all periodic patterns are dominant and if it differs between households."}
elec <- read_rds(here("paper/data/elec.rds")) %>% 
  filter(date >= ymd("20180101"), date < ymd("20180701"))
rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")

elec <- elec %>% 
  mutate(
    wday = wday(date, label = TRUE, week_start = 1),
    weekday = if_else(wday %in% c("Sat", "Sun"), "Weekend", "Weekday")
  )
p_cal_elec <- elec %>% 
  filter(id %in% c(2, 4)) %>% 
  frame_calendar(x = time, y = kwh, date = date, nrow = 1) %>% 
    ggplot(aes(x = .time, y = .kwh, group = date)) +
    geom_line(aes(colour = as.factor(id)), size = 0.5) +
    scale_colour_brewer(name = "", palette = "Dark2", direction = 1) +
    facet_grid(id ~ ., labeller = label_both) +
    theme(legend.position = "bottom")
prettify(p_cal_elec, size = 2.5, label.padding = unit(0.1, "lines"))
```

@@

id2_tsibble <- elec %>% 
   filter(id == 2) %>% 
   as_tsibble(index = date_time)

id4_tsibble <- elec %>% 
   filter(id == 4) %>% 
   as_tsibble(index = date_time)

# hour-of-day and month-of-year (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
p1 <- id2_tsibble %>%
   prob_plot("month_year",
             "hour_day",
             response = "kwh",
             plot_type = "quantile",
             symmetric = TRUE,
             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
  ggtitle("") + theme(
        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
  scale_colour_brewer(name = "", palette = "PiYG")

p2 <- id4_tsibble %>%
   prob_plot("month_year",
             "hour_day",
             response = "kwh",
             plot_type = "quantile",
             symmetric = TRUE,
             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) + 
  ggtitle("a") + theme(
        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))

p3 <- id2_tsibble %>%
  create_gran("week_month") %>% 
  filter(week_month != 5) %>% 
   prob_plot("wknd_wday",
             "week_month",
             response = "kwh",
             plot_type = "quantile",
             symmetric = FALSE,
             quantile_prob = c(0.25,0.5,0.75)) +
   ggtitle("") +

        theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))

p4 <- id4_tsibble %>%
    create_gran("week_month") %>% 
  filter(week_month != 5) %>% 
   prob_plot("wknd_wday",
             "week_month",
             response = "kwh",
             plot_type = "quantile",
             symmetric = FALSE,
             quantile_prob = c(0.25,0.5,0.75)) +
  ggtitle("b") +  #+ scale_x_discrete(breaks = seq(0, 23, 4)) + 
theme(
        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))

@@

```{r}
id2_tsibble %>%
  create_gran("month_year") %>% 
  ggplot() +
  geom_lv(aes(x = month_year, y = kwh))

   prob_plot("month_year",
             "hour_day",
             response = "kwh",
             plot_type = "quantile",
             symmetric = TRUE,
             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
  ggtitle("") + theme(
        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
  scale_colour_brewer(name = "", palette = "PiYG")
```

```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day for id2 (left) and id4 (right). The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile. Difference between the 90th and 75th quantiles is less for (Jan, Feb) in id2 suggesting that it is a more frequent user of air conditioner than id4. Energy consumption for id2 changes across both granularities, whereas for id4 daily pattern stays same irrespective of the months."}
ggpubr::ggarrange(p1, p2, ncol = 2)
```

```{r id4, fig.cap = "something2", eval = FALSE}
ggpubr::ggarrange(p3, p4, ncol = 2)
```

@@

sim_varall_normal <- function(nx, nfacet, mean, sd, w) {
  dist_normal((mean + seq(0,
    (nx *
      nfacet - 1),
    by = 1
  ) * w), sd)
}
sim_panel_varall <- sim_panel(
  nx = 2, nfacet = 3,
  ntimes = 500,
  sim_dist = sim_varall_normal(2, 3, 5, 10, 5)
) %>% unnest(data)

p_varall <- sim_panel_varall %>%
  rename("facet level" = "id_facet" ) %>% 
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
  facet_wrap(~`facet level`,labeller = "label_both") + 
  geom_boxplot() +
  ggtitle("") +
  xlab("x level") +
  ylab("")

sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
 }

sim_panel_varx <- sim_panel(
   nx = 2, nfacet = 3,
   ntimes = 500,
   sim_dist = sim_varx_normal(2, 3, 5, 10, 5)
 ) %>% unnest(data)

p_varx <- sim_panel_varx %>%
  rename("facet level" = "id_facet" ) %>% 
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
  facet_wrap(~`facet level`,labeller = "label_both") + 
  ggtitle("") +
  geom_boxplot() +
  xlab("x level") +
  ylab("simulated response")

sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
  rep(dist_normal((mean + seq(0, nfacet - 1, by = 1) * w), sd), each = nx)
}

sim_panel_varf <- sim_panel(
  nx = 2, nfacet = 3,
  ntimes = 500,
  sim_dist = sim_varf_normal(2, 3, 5, 10, 5)
) %>% unnest(data)

p_varf <- sim_panel_varf %>%
  rename("facet level" = "id_facet" ) %>% 
  ggplot(aes(x = as.factor(id_x), y = sim_data)) +
  facet_wrap(~`facet level`,labeller = "label_both") + 
  geom_boxplot() +
  ggtitle("") +
  xlab("x level") +
  ylab("")

sim_panel_null <- sim_panel(
   nx = 2,
   nfacet = 3,
   ntimes = 500,
   sim_dist = distributional
   ::dist_normal(5, 10)
) %>% unnest(c(data))

set.seed(9999)

p_null <- sim_panel_null %>%
  rename("facet level" = "id_facet" ) %>% 
  ggplot(aes(x = as.factor(id_x), y = sim_data)) +
  facet_wrap(~`facet level`,labeller = "label_both") +
  geom_boxplot() +
  ggtitle("") +
  xlab("x level") +
  ylab("simulated response")

ggpubr::ggarrange(p_null, p_varf,  p_varx, p_varall, nrow = 2, ncol = 2,
                  common.legend = TRUE,
                  labels = c("a", "b", "c", "d"))

@@

```{r}
d1 <- tibble (variable = c("nx", "nfacet", "$N_C$", "$H_{N_C}$", "$lambda$", "$omega$", "$wpd$","$nperm$", "$nsim$"),  description = c("number of x categories", "number of facet categories","number of cyclic granularities", "set of harmonies", "tuning parameter", "mean increment", "raw distance measure", "number of permutations for threshold/normalization", "number of simulations"))

d2 <- tibble(variable =  c("$wpd_{norm}$", 
                           "$wpd_{threshold}$",
                           "$D_{null}$",
                           "$D_{var_f}$", 
                           "$D_{var_x}$",
                           "$D_{var_{all}}$"), 
             description = c("normalized distance measure",
                             "threshold for significance",
                             "null design",
                             "design with varying facets only", 
                             "design with varying x only", 
                             "design with varying both facets and x"))

d <- bind_rows(d1, d2)
knitr::kable(d, format = "markdown", escape = FALSE, caption = "Nomenclature table")

@@

```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets. The dotted lines represent the distances between different categories. Panel 1) and 2) show the between-facet distances. Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively. When categories are ordered, distances should only be considered for consecutive x-axis categories. Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
```

@@

```{r raw, fig.cap = "Distribution of $wpd$ is plotted across different $nx$ and $nfacet$ categories under $D_{null}$. Both shape and scale of the distribution changes for different comparisons. This is not desirable since under null design, the distribution of the distance measure is not expected to capture any differences."}
G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")

G21 %>% 
  ggplot(aes(x = value)) + 
  geom_density(fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
  xlab("wpd")
```

```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$. The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$. Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$."}
G21 %>% 
  ggplot(aes(x=nx*nfacet, y = value)) +
  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("wpd")

@@

@@

```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories. Both shape and scale of the distributions are now similar for different panels under the null design."}
G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds"))

G21_norm %>% 
  ggplot(aes(x = value)) + 
  geom_density(fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
  xlab("wpd normalised using permutation approach")
```

@@

```{r linear-model, message=FALSE}
G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))

G21_median <- G21 %>% 
  group_by(nx*nfacet) %>% 
  summarise(actual = median(value))

# fit model median to log(nx*nfacet)
fit_lm2 <- lm(actual ~ log(`nx * nfacet`) , data = G21_median)

broom::tidy(fit_lm2) %>% kable(caption = "Results of linear model to capture the relationship between wpd and number of comparisons.")
```

@@

```{r resi-linear, fig.cap = "$wpd_{norm}^{linear}$ which are defined as the residuals of the linear model have mean zero and are homogenous. Further, by design they are independent of the $nx*nfacet$ and hence could be a potential candidate for $wpd_norm$."}

intercept <- fit_lm2$coefficients[1]
slope <- fit_lm2$coefficients[2]

G21 %>% 
  ggplot(aes(x=log(nx*nfacet), y = (value - slope*log(nx*nfacet)))) +
  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
  ylab("wpd normalised using linear modelling approach")
```

@@

```{r wpd-glm-horizontal, echo = FALSE, message=FALSE, fig.caption = "$wpd_{glm}$ is plotted against log(nx*nfacet) and this transformation causes the median of $wpd_{glm}$ to have no relationship with log(nx*nfacet)"}

G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))

G21_median <- G21 %>% 
  group_by(nx*nfacet) %>% 
  summarise(actual = median(value))

glm_fit <- glm(actual ~ log(`nx * nfacet`),
              family = Gamma(link = "inverse"),
              data = G21_median)

intercept <- glm_fit$coefficients[1]
slope <- glm_fit$coefficients[2]

G21_sd  = G21 %>% 
    mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
    )
    )
    ))

scale_fac <- 1/G21_sd$wpd_glm %>% sd()

# checking the fit of the residuals from glm fit

# fitted_glm <- fitted(glm_fit, type = "response")
# residuals <- residuals.glm(glm_fit, type = "response")
# hist(residuals)

#h = augment(glm_fit)
# ggplot(h) +
#   geom_histogram(aes(x = .resid))

# residual <- G21_median$actual  - fitted_glm
# 
# hist(residual)

G21 %>% 
  ggplot(aes(x=log(nx*nfacet),
             y = (value - (1/(intercept + slope*log(nx*nfacet)
                    )
                    )
             )
  )
  ) +
  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
  ylab("wpd_glm = wpd - 1/(a  + b*log(nx*nfacet))")
```

@@

G21_glm <- G21 %>% 
  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
                    )
                    )
             ),
         wpd_glm_scaled = ((wpd_glm*320)))

#G21_glm$wpd_glm_scaled %>% sd()

G21_glm %>% 
  ggplot() +
  geom_density(aes(x = wpd_glm), 
                   fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") 
```

@@

```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted. In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis. The distribution looks symmetric and looks like normal except in the tails."}
hist <- ggplot(G21_glm) +
  geom_histogram(aes(x = wpd_glm_scaled)) +
  ggtitle("a") + xlab("transformed wpd using glm approach")

p <- ggplot(G21_glm, aes(sample = wpd_glm_scaled))
qqplot <-  p + geom_qq() + geom_qq_line() + coord_fixed(ratio = 4/5) +
  ggtitle("b")

# G21_glm <- G21 %>% 
#     mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
#     )
#     )
#     ),
#     wpd_glm_scaled = 300*(wpd_glm))

 # G21_glm$wpd_glm_scaled %>% 
 #   range()
hist + qqplot
```

@@

G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
  rename("wpd_permutation" = "value")

# G21_model_data <- G21 %>%
#   mutate(model =
#            ((1/value)
#                   - intercept -
#                     slope*log(nx*nfacet))/slope) %>%
#   mutate(model_trans =
#            (model - mean(model))/sd(model))

# G21_model_data$model %>% summary()

G21_all_data <- G21_permutation %>% 
  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
  pivot_longer(cols = c(3, 7),
               names_to = "type_estimate",
               values_to = "value_estimate")
G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))

G21_all_data %>% 
  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
  ggplot() +
  geom_density(aes(x = value_estimate, 
                   fill = type_estimate), alpha = 0.5) +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") +
  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
  xlab("wpd_norm2") +
  scale_x_continuous(breaks = c(-5, -3, 0, 3, 5))

# G21_all_data %>% 
#   filter(type_estimate %in% c("wpd_permutation", "wpd_glm")) %>% 
#   ggplot() +
#   geom_density(aes(x = value_estimate, 
#                    fill = type_estimate), 
#                alpha = 0.7) +
#   facet_grid(nx~nfacet,
#              labeller = "label_both") +
#   theme(legend.position = "bottom") +
#   scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
#   xlab("wpd_norm2")

# are scales same
# 
# G21_model_data %>%
#   group_by(nx, nfacet) %>% 
#   summarize(sd_model = sd(model))
#   
# G21_all_data %>%
#   filter(type_estimate == c("perm_trans")) %>% 
#   select(value_estimate) %>% 
#   range()
# 
# G21_all_data %>%
#   filter(type_estimate == c("wpd_glm_scaled")) %>% 
#   select(value_estimate) %>% 
#   range()
```

@@

sim_varall_normal <- function(nx, nfacet, mean, sd, w) {
  dist_normal((mean + seq(0,
    (nx *
      nfacet - 1),
    by = 1
  ) * w), sd)
}
sim_panel_varall <- sim_panel(
  nx = 2, nfacet = 3,
  ntimes = 500,
  sim_dist = sim_varall_normal(2, 3, 0, 1, 10)
) %>% unnest(data)

set.seed(9999)
varall <- compute_pairwise_norm(sim_panel_varall, 
                           gran_x = "id_x",
                           gran_facet = "id_facet",
                           response = sim_data, 
                           nperm = 200
)

# plot
p_varall <- sim_panel_varall %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
  ggtitle(paste("d", round(varall, 2))) + xlab("x level")
```

```{r varx-new}
sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
 }

sim_panel_varx <- sim_panel(
   nx = 2, nfacet = 3,
   ntimes = 500,
   sim_dist = sim_varx_normal(2, 3, 0, 1, 10)
 ) %>% unnest(data)

set.seed(9999)
varx <- compute_pairwise_norm(sim_panel_varx, 
                           gran_x = "id_x",
                           gran_facet = "id_facet",
                           response = sim_data, 
                           nperm = 200
)

# plot
p_varx <- sim_panel_varx %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
    ggtitle(paste("c", round(varx, 2))) + xlab("x level")
```

```{r varf-new}
sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
  rep(dist_normal((mean + seq(0, nfacet - 1, by = 1) * w), sd), each = nx)
}
sim_panel_varf <- sim_panel(
  nx = 2, nfacet = 3,
  ntimes = 500,
  sim_dist = sim_varf_normal(2, 3, 0, 1, 10)
) %>% unnest(data)

set.seed(9999)
varf <- compute_pairwise_norm(sim_panel_varf, 
                           gran_x = "id_x",
                           gran_facet = "id_facet",
                           response = sim_data, 
                           nperm = 200
)

p_varf <- sim_panel_varf %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
    ggtitle(paste("b", round(varf, 2))) + xlab("x level")
```

```{r null-new}
sim_panel_null <- sim_panel(
   nx = 2,
   nfacet = 3,
   ntimes = 500,
   sim_dist = distributional
   ::dist_normal(0, 1)
) %>% unnest(c(data))

set.seed(9999)

null <- compute_pairwise_norm(sim_panel_null, 
                           gran_x = "id_x",
                           gran_facet = "id_facet",
                           response = sim_data, 
                           nperm = 200
)

p_null <- sim_panel_null %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
    ggtitle(paste("a", round(null, 2))) + xlab("x level") 
```

```{r plot-all-new3, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here. As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d). Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design."}
library(patchwork)
(p_null + p_varf)/(p_varx + p_varall)
```

>>>>

---
title: A new metric for automatic data visualization for distributional difference in time series

@@

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE,
        tinytex.verbose = FALSE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
#                                                     read_chunk('main.R')
#knitr::read_chunk(here::here("paper/R/", "null_distribution.R"))
#knitr::read_chunk(here::here("paper/R/", "mean_null.R"))
#source(here::here("paper/R/sim_panel.R"))
# Set up plan
#source("_drake.R")
# Run all code required
#drake::r_make()
# load each object as required
# loadd()
```

```{r external, include = FALSE, cache = FALSE}
read_chunk("paper/scripts/main.R")
```

```{r load}
```

@@

```{r calendar-elec, fig.height = 8, fig.cap = "Calendar displays faceted by two households are shown. The calendar displays are rich in information and has several components. For example, it can be observed easily that the level of energy consumption by household 2 is higher than household 4. Also, it gives an overview on when these households are away for holidays and which months consumptions are highest (Jan, Feb). However, when it comes to discerning periodic patterns, analyzing all possible periodic patterns through this display is overwhelming due to combination of linear and cyclic representation of time. For example, there is more going on in terms of peaks and troughs in id 2 compared to id 4, but it is not clear which all periodic patterns are dominant and if it differs between households."}

@@

@@

```{r}
id2_tsibble %>%
  create_gran("month_year") %>%
   prob_plot("month_year",
             "hour_day",
             response = "kwh",
             plot_type = "quantile",
             symmetric = TRUE,
             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
  ggtitle("") + theme(
        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
  scale_colour_brewer(name = "", palette = "PiYG")
```

```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day for id2 (left) and id4 (right). The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile. Difference between the 90th and 75th quantiles is less for (Jan, Feb) in id2 suggesting that it is a more frequent user of air conditioner than id4. Energy consumption for id2 changes across both granularities, whereas for id4 daily pattern stays same irrespective of the months."}
```

```{r id4, fig.cap = "something2", eval = FALSE}

@@

@@

```{r notations}

@@

```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets. The dotted lines represent the distances between different categories. Panel 1) and 2) show the between-facet distances. Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively. When categories are ordered, distances should only be considered for consecutive x-axis categories. Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}

@@

```{r raw, fig.cap = "Distribution of $wpd$ is plotted across different $nx$ and $nfacet$ categories under $D_{null}$. Both shape and scale of the distribution changes for different comparisons. This is not desirable since under null design, the distribution of the distance measure is not expected to capture any differences."}

@@

```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$. The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$. Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$."}
```

@@

```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories. Both shape and scale of the distributions are now similar for different panels under the null design."}
```

@@

```{r linear-model, message=FALSE}

@@

```{r resi-linear, fig.cap = "$wpd_{norm}^{linear}$ which are defined as the residuals of the linear model have mean zero and are homogenous. Further, by design they are independent of the $nx*nfacet$ and hence could be a potential candidate for $wpd_norm$."}
```

@@

@@

@@

```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted. In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis. The distribution looks symmetric and looks like normal except in the tails."}

@@

@@

```{r varx-new}

```{r varf-new}
```

```{r null-new}

```{r plot-all-new3, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here. As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d). Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design."}
